---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Here we load the file, unzip the file, and read the file into a dataframe. This produces a dataframe with columns *steps*, *date*, and *interval*.
```{r}
# Zip file name
zfile <- "activity.zip"

# Unzip file
ufile <- unzip(zfile)

# Read unzipped file to dataframe
df <- read.csv(ufile, sep = ',', stringsAsFactors = FALSE, header = TRUE)

# Return the first part of the dataframe object
head(df)
```

We then transform the date fields from character to date objects.
```{r}
# Transform dates from character to date objects
df$date <- as.Date(df$date)
```


## What is mean total number of steps taken per day?

We first calculate the daily steps.
```{r}
# Summarize daily steps
dailySteps <- aggregate(steps ~ date, data = df, sum)
```

We then graph the daily counts with a bar chart (histogram) to see daily trends.
```{r dailycount}
library(ggplot2)
ggplot(data = dailySteps, aes(date, steps)) + geom_bar(stat = "identity")
```

To understand daily averages, we calculate the mean and median daily steps.
```{r}
# Calculate the mean daily steps
mean(dailySteps$steps)

# Calculate the median daily steps
median(dailySteps$steps)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
